### 2015-08-13 Manuscript/BiologyLetters/Missing_mammals-draft.tex
Figures updates

%---------------------------------------------
%
%       ABSTRACT
%
%---------------------------------------------
\newpage
\begin{abstract}
\section{abstract} % NC: Just put this here as it then separates this for the word count
Analyses of living and fossil taxa are crucial for understanding changes in biodiversity through time.
The Total Evidence method allows living and fossil taxa to be combined in phylogenies, by using molecular data for living taxa and morphological data for both living and fossil taxa.
With this method, substantial overlap of morphological data among living and fossil taxa is crucial for accurately inferring topology.
However, although molecular data for living species is widely available, scientists using and generating morphological data mainly focus on fossils.
Therefore, there is a gap in our knowledge of neontological morphological data even in well-studied groups such as mammals.

@@

%\noindent Key words: Total Evidence method, phylogenetic clustering, morphological matrix, extinct, topology\\ Excluded from word count.
% NC: Might need some new ones as these are in the abstract now...

@@

%Biology letters various stuff
\section{Ethics statement}
\section{Data accessibility statement}
All data and analysis code is available on GitHub (\url{https://github.com/TGuillerme/Missing_living_mammals}).
\section{Authors' Contributions}
T.G. and N.C conceived and designed the experiments. T.G. performed the experiments and analysed the data. T.G. and N.C. contributed to the writing of the manuscript. All authors approved the final version of the manuscript.
\section{Competing Interests}
We have no competing interests.
\section{Acknowledgments}
We thank David Bapst, Graeme Lloyd, Nick Matzke and April Wright.
\section{Funding statement}
This work was funded by a European Commission CORDIS Seventh Framework Programme (FP7) Marie Curie CIG grant (proposal number: 321696).

>>>>

%---------------------------------------------
%
%       ABSTRACT
%
%---------------------------------------------
\newpage
\begin{abstract}
%\section{abstract} % NC: Just put this here as it then separates this for the word count
Analyses of living and fossil taxa are crucial for understanding changes in biodiversity through time.
The Total Evidence method allows living and fossil taxa to be combined in phylogenies, by using molecular data for living taxa and morphological data for both living and fossil taxa.
With this method, substantial overlap of morphological data among living and fossil taxa is crucial for accurately inferring topology.
However, although molecular data for living species is widely available, scientists using and generating morphological data mainly focus on fossils.
Therefore, there is a gap in our knowledge of neontological morphological data even in well-studied groups such as mammals.

@@

\noindent Key words: Total Evidence method, phylogenetic clustering, morphological matrix, extinct, topology\\
% NC: Might need some new ones as these are in the abstract now...

@@

%Biology letters various stuff
\section{Ethics statement}
N/A
\section{Data accessibility statement}
All data and analysis code is available on GitHub (\url{https://github.com/TGuillerme/Missing_living_mammals}).
\section{Authors' Contributions}
T.G. and N.C conceived and designed the experiments. T.G. performed the experiments and analysed the data. T.G. and N.C. contributed to the writing of the manuscript. All authors approved the final version of the manuscript.
\section{Competing Interests}
We have no competing interests.
\section{Acknowledgments}
We thank David Bapst, Graeme Lloyd, Nick Matzke and April Wright.
\section{Funding statement}
This work was funded by a European Commission CORDIS Seventh Framework Programme (FP7) Marie Curie CIG grant (proposal number: 321696).
